Supervised Learning for Psychological Attention to High School Students

### 2020-11-11 article/article.tex
[ article ] Added authors and abstract.
[ article ] Added sections.
[ article ] added introduction

%%%%%%%% START DOCUMENT

\title{}
\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}
\date{\today}

@@

\textit{Note}: All the code and the latex file can be found in
\href{https://github.com/juanscr/ai-works}{the github repository}.

>>>>

%%%%%%%% START DOCUMENT
\title{Supervised Learning for Psychological Attention to High School Students}

\author{\IEEEauthorblockN{Juan S. Cárdenas-Rodríguez}
  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
    \textit{EAFIT University}\\
    Medellín, Colombia \\
    jscardenar@eafit.edu.co} \and \IEEEauthorblockN{David Plazas}
  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
    \textit{EAFIT University}\\
    Medellín, Colombia \\
    dplazas@eafit.edu.co} }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Hello.
\end{abstract}

\begin{IEEEkeywords}
  Nice.
\end{IEEEkeywords}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textit{Note}: All the code and the latex file can be found in
\href{https://github.com/juanscr/ai-works}{the GitHub repository}.

\section{Introduction}

Mental health is crucially important for every human being and has become one of
the most important issues surrounding human health. According to the World
Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001 report.}}
report of 2001, mental disorders can affect 25\% of the population, therefore,
suggesting the ongoing trend of people suffering from lack of mental health.
Additionally, with the recent events caused by the COVID-19 pandemic, mental issues
have risen as consequence of lockdowns all around the globe, as have been proved by 
recent studies \parencite{rossi2020,xiong2020}.

Furthermore, mental health is more important to monitor in adolescents and kids
as this group is in the process of developing their mental structure and
character. In this manner, as they continue creating their view about the world
they must be surrounded by a healthy environment that promotes healthy habits
and relationships with their surroundings.

As a result, schools and parents have an important responsibility to the
students of creating this environment and wisely handling mental health issues.
However, high schools do not always know how to handle or detect cases of mental
health issues. Additionally, technology has led to targeted harassing becoming
more popular over time, therefore, difficulting the probability of detecting
these cases.

Some of the most common and important mental health issues are anxiety,
depression, and hyperkinetic disorder. According to \textcite{schulte2016}, around
10\% to 20\% of children suffer from hyperkinetic disorder. Additionally, school
teachers just assume this disorder is a cause of undisciplined students and can
take the hyperkinetic student to a depressive state. These three mental
disorders can leave severe damage to a kid and can lead them to suicide.

Hence, it is of the utmost importance to quickly and efficiently detect students
that might be having a mental health issue to immediately start a process with
him/her. Furthermore, this detection has to be done with measurable variables
that can be easily obtained from questionnaires or school data.

The present work is oriented to the application of supervised learning techniques
(decision trees, support vector machines and neural networks) for classifying the
data from the survey, aiming for the construction of a model to detect 
individuals with mental health issues. This document is organized as follows: 
Section \ref{sec:start} gives a short review of the current literature of 
supervised techniques in this application area, Section \ref{sec:meth} shows 
the general methodology used in this work, moreover Section \ref{sec:res} shows 
the obtained results over the data and slight modifications, finally Section 
\ref{sec:conc} concludes this work and sets pillars for future works.

\section{State of the Art}\label{sec:start}

\section{Methodology}\label{sec:meth}

\section{Results}\label{sec:res}

\section{Conclusions}\label{sec:conc}
